Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-05-15 RNARedPrint-Bioinfo2018.tex
Highlight notes by macro Final (in red)
Update on Overleaf.
fix centering figure

\usepackage[scale=.95]{inconsolata}

@@

\newcommand{\Final}[1]{#1}
%% Uncomment the line below for ``Final'' version
%\renewcommand{\Final}[1]{}

@@

\begin{figure*}[t]
{\centering\includegraphics[width=.8\textwidth]{Figs/Workflow}\\}
\caption{General outline of \ourprog{} for base pair-based energy models. From a set of target secondary structures (i), base-pairs are merged (ii) into a (base pair) dependency graph (iii) and transformed into a tree decomposition (iv). The tree is then used to compute the partition function, followed by a Boltzmann sampling of valid sequences (v). An adaptive scheme learns weights to achieve targeted energies and \GCb\%, leading to the production of suitable designs (vi).}
\label{fig:workflow}
\end{figure*}

@@

\begin{table}[t]
\centering
\medskip
\begin{tabular}{@{}>{\bf}l@{\quad}>{\tt}l@{\quad}@{\quad}c@{\quad}c@{\quad}c@{}}
             &   \textbf{\textrm{Dataset}}   & {\bfseries\ourprog{}} & \textbf{Uniform} & \textbf{Improvement} \\\toprule
  Seeds      & 2str & 21.67 ($\pm$4.38) & 37.74 ($\pm$6.45) & 73\%\\
             & 3str & 18.09 ($\pm$3.98) & 30.49 ($\pm$5.41) & 71\%\\
             & 4str & 19.94 ($\pm$3.84) & 32.29 ($\pm$5.24) & 63\%\\\midrule

>>>>

\usepackage{inconsolata}

@@

\newcommand{\Final}[1]{\begingroup\color{red!70!black}#1\endgroup}
%% Uncomment the line below for ``Final'' version
%\renewcommand{\Final}[1]{}

@@

\begin{figure*}[t]
\begin{center}
    \includegraphics[width=.8\textwidth]{Workflow.pdf}
\end{center}
\caption{General outline of \ourprog{} for base pair-based energy models. From a set of target secondary structures (i), base-pairs are merged (ii) into a (base pair) dependency graph (iii) and transformed into a tree decomposition (iv). The tree is then used to compute the partition function, followed by a Boltzmann sampling of valid sequences (v). An adaptive scheme learns weights to achieve targeted energies and \GCb\%, leading to the production of suitable designs (vi).}
\label{fig:workflow}
\end{figure*}

@@

\begin{table}[t]
\centering
\medskip
\begin{tabular}{@{}>{\bf}l@{\quad}>{\tt}l@{\quad}@{\quad}c@{\quad}c@{\quad}c@{}}
             &   \textbf{\textrm{Dataset}}   & {\bfseries\ourprog{}} & \textbf{Uniform} & \textbf{Improvement} \\\toprule
  Seeds      & 2str & 21.67 ($\pm$4.38) & 37.74 ($\pm$6.45) & 73\%\\
             & 3str & 18.09 ($\pm$3.98) & 30.49 ($\pm$5.41) & 71\%\\
             & 4str & 19.94 ($\pm$3.84) & 32.29 ($\pm$5.24) & 63\%\\
             & PK60 & 19.94 ($\pm$3.84) & 32.29 ($\pm$5.24) & 63\%\\
             & PK80 & 19.94 ($\pm$3.84) & 32.29 ($\pm$5.24) & 63\%\\
             & 4str & 19.94 ($\pm$3.84) & 32.29 ($\pm$5.24) & 63\%\\
             \midrule
